---
title: "Reproducible Research: Peer Assessment 1"
output: 
  html_document:
    keep_md: true
---


## Loading and preprocessing the data

``` {r, echo = TRUE}
library(ggplot2)
library(lubridate, warn.conflicts = FALSE)
library(dplyr, warn.conflicts = FALSE)

unzip("activity.zip")
data <- read.csv("activity.csv")
data$date <- ymd(data$date)
head(data)
```

## What is mean total number of steps taken per day?

``` {r, echo = TRUE}
steps_per_day <- data %>%
                 group_by(date) %>%
                 summarise(steps = sum(steps, na.rm = TRUE))
head(steps_per_day)

g <- ggplot(data = steps_per_day, aes(x = steps))
g + geom_histogram(bins = 15) 
### Mean of the total number of steps taken per day
mean(steps_per_day$steps, na.rm = TRUE)
### Median of the total number of steps taken per day
median(steps_per_day$steps, na.rm = TRUE)
```

## What is the average daily activity pattern?

``` {r, echo = TRUE}
minute_summarise <- data %>%
                    group_by(interval) %>%
                    summarise(steps = mean(steps, na.rm = TRUE))
ggplot(data = minute_summarise, aes(x = interval, y = steps)) + geom_line()
### 5-minutes interval, that contain the maximum numbers of steps on interval, on average across all days
minute_summarise[[which.max(minute_summarise$steps), "interval"]]
```

## Imputing missing values

``` {r, echo = TRUE}
print("Numbers of NA")
sum(is.na(data$steps))
sum(is.na(data$date))
sum(is.na(data$interval))
### As you can see, only steps column contains NA values
```

As one of the main point is to find the relationship between time and activity(amount of steps), it's better to keep 
mean 5-minutes activities the same. So let's fill NA with mean steps per 5-minutes mean steps

``` {r, echo = TRUE}
filled_data <- data
na_row <- which(is.na(filled_data$steps))
### Filling na with mean steps(averaged per day)
for(row in na_row){
    filled_data[row, "steps"] = 
        minute_summarise[minute_summarise$interval == filled_data[row, "interval"], "steps"]
}
### Averaged per days

steps_per_day_f <- filled_data %>%
                   group_by(date) %>%
                   summarise(steps = sum(steps))

g <- ggplot(data = steps_per_day_f, aes(x = steps))
g + geom_histogram(bins = 15) 

###Mean

mean(steps_per_day_f$steps)

### Median

median(steps_per_day_f$steps)


#### The result is't differ much from data with NA's. Histobram is the same, but has more obervations. Also less 0 because NA was filled
```

## Are there differences in activity patterns between weekdays and weekends?

``` {r, echo = TRUE}
filled_data <- mutate(filled_data, date_type = factor(wday(date) == 1 | wday(date) == 7, labels = c("weekday", "weekend")))
minute_summarise <- filled_data %>%
                    group_by(date_type, interval) %>%
                    summarise(steps = mean(steps, na.rm = TRUE), )
qplot(interval, steps, data = minute_summarise, geom = "line", facets = date_type ~ .)
```
